MCC Models

### 2019-10-04 papers/full_paper/Supplementary_information.Rmd
update manuscript

---
title             : "Supplementary information: Pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
shorttitle        : "Pragmatic cue integration: Supplementary information"

>>>>

---
title             : "Supplementary information: Predicting pragmatic cue integration in adults’ and children’s inferences about novel word meanings"
shorttitle        : "Predicting pragmatic cue integration: Supplementary information"
